Untitled

### 2020-05-01 results/README.Rmd
Update manuscript and dataset table

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
```

Script for reading simulation files
```{python}

@@

Script for reading results 
```{r}
data <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
statspath <- paste0("statistics/one/RCTD/", "testoutput_RCTD_one_", data, ".json")

ace <- fromJSON(file = statspath[1])

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
library(tidyverse)
library(knitr)
```

Script for reading simulation files
```{python}
# to be found on harddrive results folder
```

Script for reading results 
```{r}
data <- readRDS("../simulation_study/R/00_datasets.RDS")
models <- list.files("/Volumes/Gerbrich/asreview/results/one/statistics/")
names(models) <- c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )

# function that reads results for a model M 
read_results <- function(m){
   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one/statistics/", m), recursive = TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,1]
  # read data
  dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one/statistics/", m, "/", x)))

  # extract wss, rrf, and loss
  dat <- map(dat, `[`, c("wss", "rrf", "loss"))

  # transorm into dataframe
  dat <- map_dfr(dat, ~ as.data.frame(.x), .id = "dataset")

  # add model name
  dat <- dat %>% 
    mutate(model = names(models[models == m]))

  return(dat)
}
```

Parse 
```{r, eval = FALSE}
dat$virus
# extract only wss, rrf, and loss values from list
test <- map(dat, `[`, c("wss", "rrf", "loss"))
# transorm into dataframe
test <- map_dfr(test, ~ as.data.frame(.x), .id = "dataset")
# add model name
test <- test %>% mutate(model = "NB + TF-IDF")
```

Apply over all datasets and models 
```{r}
# extract results for all models
# list for models separately
results <- lapply(models, read_results)

# all in one dataframe
results <- do.call("rbind", results)
results %>%
  group_by(dataset) %>%
  arrange(loss)
```

Create table
```{r}
library(tables)
library(data.table)
library(gt)
library(tidyr)
library(tidyverse)
tabres <- 
  results %>%
  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))

@@

```{r}
library(expss)

test <- results %>% pivot_longer(cols = c(starts_with("wss"), starts_with("rrf"), "loss"), names_to = "stats", values_to = "value")

tab <- 
  test %>%
  tab_rows(model) %>%
  tab_cells(value) %>%
  tab_cols(dataset %nest% stats) %>%
  tab_stat_mean() %>%
  tab_pivot()

@@

```{r}
tabres %>%
  select(model, starts_with("wss.95"), starts_with("loss"))

gtest <- tabres %>%
  gt()

gtest <- results %>%
  gt() %>%

```
```{r}
library(flextable)
typology <- data.frame(
  col_keys = names(results)[2:43],
  what = rep(data,7),
  measure = rep(c("WSS@95", "WSS@99", "WSS@100", "RRF@5", "RRF@10", "RRF@20", "ATD"), each = )
  what = c(rep("WSS", 3), rep("RRF", 3), "loss"),
  measure = c("95", "99", "100", "5", "10", "20", "0"),
  stringsAsFactors = FALSE
)

test <- flextable(tabres)
test <- set_header_df(test, mapping = typology, key = "col_keys")
merge_h(test, part = "header")
```

Now again for with seed 
```{r}
#files = list.files("/Volumes/Gerbrich/asreview/results/one/statistics/", recursive = TRUE)
